Contextual Identity: Towards Usable Privacy

### 2013-03-03 paper.tex
never-ending rewrites

\section{Contextual identity violations}
In this section we discuss three types of \textit{contextual identity
violations}. We consider a contextual identity violation to be when multiple
identities are linked without user intent, or when the user cannot choose which
contextual identity to assert in a given situation. In these examples the user
may not be conscious of what a contextual identity is: nevertheless each
example illustrates a loss of user control over what aspects of self to
reveal in a given context.

@@

\subsection{Policy errors}
\label{sec:policies}
Some service providers have policies which preclude isolating multiple
contextual identities. For example, Facebook and Google have a ``Real Names''
policy, which requires users to register for accounts with their legal
name~\cite{fb_names,google_names}.  These policies ignore that
community-building happens in many different contexts, that users have many
legitimate reasons for presenting different identities in different contexts,
and that users don't necessarily want those identities to be linked. For
example, disallowing avatar handles as a primary identifier makes building a
gaming community difficult.  Linking a gaming identity to a professional
identity has already caused problems for 2012 Maine Senate candidate and World
of Warcraft gamer Colleen Lachowicz~\cite{maine}.

It is impossible for users who want to isolate multiple contextual identities
to participate in these networks without violating the terms of service.  The
``Real Names'' policy prohibits users from asserting control over their
identity.

Even worse, many of these providers now serve as login platforms for external
sites. For example, Facebook Connect allows third-party websites to
authenticate users using their Facebook identity~\cite{fb_connect}.  Because it
is against the terms of service to have multiple Facebook accounts, using
Facebook Connect has the unwanted side-effect of linking multiple contextual
identities across multiple sites.

@@

\section{Research directions}
We propose new research directions based on the following questions.
\begin{itemize}
\item How do users think about identity?
\item How do users manage identity?
\item How can we improve tools for managing identity?
\end{itemize}

@@

\begin{itemize}
\item How is identity represented online?
\item What do you need to represent your identity?
\item Is your identity tied to your device?
\item If you check your mail, read news, log on to a social network at a
computer at the public library, does that affect your identity?
\item What does it mean to share devices? If you lend your tablet to your
sister, is she representing herself, or you?
\item If you register for an account on a service, do you expect that to have
an influence on your online identity? What if you never use that account again?
\item If you visit a website, do you expect that to have an influence on your
browsing experience or online identity? If so, for how long?
\item Which parts of your online identity do you expect to be visible to
your housemates, friends, relatives, or employers?
\item Which parts of your online identity do you expect to be visible to
websites you use? What about websites you don't use?
\item Which parts of your identity do you want to share with whom?
\item Which parts of your identity do you want to keep secret from whom?
\item How does your identity change over time?
\end{itemize}

danah boyd's work surveying youth and social networks is excellent, and Pew
Internet is a good source for self-reported phone surveys on privacy and social
media, but there is otherwise a dearth of research in these
areas~\cite{boyd,pew1,pew2,pew3}.
% digital natives is related but not exactly

@@

Users who are aware of having multiple identities engage in the following
identity management techniques.

@@

Many users have multiple devices and many use them for different purposes.
Sometimes the difference in purpose is due to the nature of the device (e.g.,
GPS and mapping software are probably more often used in mobile devices) and
some may be due to policy (e.g., personal browsing is limited to a personal
laptop). Using multiple devices implicitly creates multiple browser states and
thus multiple identities.  However, these identities may still be linked
through authentication data or other techniques~\cite{aol}.

@@

Using multiple browsers forces separation between cookies, history, builtin
password managers, and other local storage. However, several browsers support
separation of profile data natively. Firefox has a Profile Manager, but it is
so unusable that it will be removed.\footnote{See
\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.} Google Chrome
supports multiple profiles\footnote{Manage multiple users on Chrome:
\url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824}}. In
both cases, the threat model does not include users with malicious intent in
the same household.

\paragraph{Private browsing mode}
Private browsing mode exists in all major browsers, but are not a complete
solution~\cite{ABBJ10}. There is no standard behavior for private browsing
mode: interaction with extensions, treatment of cookies, history, and
bookmarks upon entering and exiting are different across browsers.
For example, entering private browsing in Firefox does not clear
cookies, history, or other session data; session data is cleared on exiting
private browsing mode. In contrast, incognito mode in Chrome makes previous
session state unavailable and clears new session state on exit; this mode
may be preferable as a ``Guest mode'' where the device owner does not want the
guest to either view or pollute existing state. L

@@

\paragraph{Controlling Information Flow}
Do Not Track is an HTTP request header that signals to the website that the
user does not want to be tracked~\cite{dnt}. Although Do Not Track is
unenforceable from the client side, service providers who ignore signal
lose reputation by acting against their users' explicit wishes.

\subsubsection{Linking identities}
\paragraph{Linking between profiles}

@@

\subsection{How can we improve identity management tools?}
\paragraph{Task inference}
If users' contextual identities are primarily task-oriented, it may be
possible to infer tasks from the user's activity. For example, the
\texttt{about:profile} Firefox extension uses the Open Directory Project and
Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.

\paragraph{Relationship inference}
Tang et al.~show that most people do not take the time to create labels and
maintain friend lists~\cite{tang}. However, the same authors show how to use
heterogeneous networks to infer relationship types (e.g., manager-subordinate)
though the graph itself is unlabeled.

\paragraph{Mitigating implicit linkage}
Given a user's contextual identities, we may be able to prevent information
leakage between them.  For example, preventing third-party cookies from being
read and set across task boundaries means that targeted ads for dating would
not follow the user when visiting a technology news site. Knowing the user's
current contextual identity also allows the browser to suppress URL bar
suggestions that aren't relevant to that identity, protecting the user from
both shoulder-surfing and distraction.

\paragraph{Mitigating explicit linkage}
Federated login services can prevent linking contextual identities to the same
user identifier. For example, Persona is the suite of tools that implements the
BrowserID protocol, and it supports multiple email
identifiers~\cite{browserid}.  If the type of service is known, Persona could
prevent the user from associating the same email identifier to radically
different contextual identities, such as ones for dating and professional use.

\paragraph{Auditing}
(needs rewrite)
A major cause of user embarrassment is exposing information to the wrong
audience. A browser is in an ideal position to intermediate social network
posts, aggregate them locally, and present them to the user when they desire to
audit their digital footprint.  For example, a user could see all of the
comments and posts they made in the last week and redact content that is
sensitive or too negative, a frequent cause of regret~\cite{wang}.  Although
this approach does not help when the service provider decides to change the
audience on the user's behalf, auditing gives the user a good opportunity to
review posts that might cause regrets. In the case of high-volume users, such a
tool could incorporate sentiment analysis to aid the user in finding
particularly problematic content.

\paragraph{Visual reminders of context}
To mitigate privacy violations caused by poor user interfaces, the software
must provide sufficient visual cues of context. For example, many but not all
Google products support multiple accounts. However, the visual cue to indicate
which account is active is a small, easy to ignore text name at the top right
of the page.

\paragraph{Expiring posts}
Humans don't have perfect memories, and perhaps social networks should not
either~\cite{delete}. Many users already engage in manual auditing and deletion
of old posts~\cite{fbtips2}. A better solution would be to build tools that let
the user manage this more easily through an API: both Twitter and Facebook
provide APIs for post deletion\footnote{Google Plus
offers a read-only API.}. One way to reduce the likelihood of linked contextual
identities would be to provide applications that expire posts after some time.

\paragraph{Expiring contextual identities}
Engaging in a long-term task such as house-buying
often requires the construction of a contextual identity. The tasks associated
with this identity have an externally imposed end date and may have long-lived
side-effects, such as long-term cookies that reveal sensitive information
(e.g., the neighborhood of the house purchase, income information derived from
purchases, other demographic data). For contextual identities that have
outlived their usefulness, users would benefit from destruction of side-effects
such as cookie data.

>>>>

\section{Contextual identity violations}
In this section we discuss three types of \textit{contextual identity
violations}. We consider a contextual identity violation to be when multiple
identities are linked without user intent, or when the user cannot choose which
identity to assert in a given context. In these examples the user
may not be conscious of what a contextual identity is: nevertheless each
example illustrates a loss of user control over what aspects of self to
reveal in a given context.

@@

\subsection{Policy errors}
\label{sec:policies}
Some service providers have policies which preclude isolating multiple
contextual identities. For example, Facebook and Google have a ``Real Names''
policy, which requires users to register for accounts with their legal
name\footnote{Facebook's policy: \url{http://www.facebook.com/help/?page=258984010787183}, Google's policy: \url{http://support.google.com/plus/bin/answer.py?hl=en&answer=1228271}}.
%\cite{fb_names,google_names}.  
These policies ignore that
community-building happens in many different contexts, that users have many
legitimate reasons for presenting different identities in different contexts,
and that users don't necessarily want those identities to be linked. For
example, disallowing avatar handles as a primary identifier makes building a
gaming community difficult. % Linking a gaming identity to a professional
%identity has already caused problems for 2012 Maine Senate candidate and World
%of Warcraft gamer Colleen Lachowicz~\cite{maine}.
It is impossible to isolate multiple contextual identities in these networks
without violating the terms of service.

Even worse, many of these providers now serve as login platforms for external
sites. For example, Facebook Connect allows third-party websites to
authenticate users using their Facebook identity~\cite{fb_connect}.  Because it
is against the terms of service to have multiple Facebook accounts, using
Facebook Connect may have the unwanted side-effect of linking multiple
contextual identities across multiple sites.

@@

\section{Research directions}
We propose new research directions based on the following questions:
\begin{itemize}
\item How do users think about identity?
\item How do users manage identity?
\item How can we improve tools for managing identity?
\end{itemize}

@@

\begin{itemize}
\item How is identity represented online?
\item What do you need to represent your identity?
\item Is your identity tied to your device?
\item If you check your mail, read news, log on to a social network at a
computer at the public library, does that affect your identity?
\item What does it mean to share devices? If you lend your tablet to your
sister, is she representing herself, or you?
\item If you register for an account on a service, do you expect that to have
an influence on your online identity? What if you never use that account again?
\item If you visit a website, do you expect that to have an influence on your
browsing experience or online identity? If so, for how long?
\item Which parts of your online identity do you expect to be visible to
your housemates, friends, relatives, or employers?
\item Which parts of your online identity do you expect to be visible to
websites you use? What about websites you don't use?
\item Which parts of your identity do you want to share or keep secret, and from whom?
\item How does your identity change over time?
\end{itemize}

Pew Internet is a good source for phone survey data on privacy and social
media and danah boyd's work on youth and social media is excellent, but there
is otherwise a dearth of research in these areas~\cite{boyd,pew1,pew2,pew3}.

@@

Users who are aware of having multiple identities engage in the following
techniques to separate, link, and curate identities.

@@

Many users have multiple devices and many use them for different purposes.
Sometimes the difference in purpose is due to the nature of the device (e.g.,
GPS and mapping software are probably more often used in mobile devices) and
some may be due to policy (e.g., personal browsing is limited to a personal
laptop). Using multiple devices implicitly creates multiple browser states and
thus multiple identities.  However, these identities may still be linked
through authentication data or other techniques.%~\cite{aol}

@@

Using multiple browsers forces separation between cookies, history, built-in
password managers, and other local storage. However, several browsers support
separation of profile data natively. Firefox 
%\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
and Chrome support multiple profiles, though neither of these is very
discoverable or easy to use.\footnote{Chrome: \url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824}, Firefox:
\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}
The threat model does not include users with malicious intent in
the same household.

\paragraph{Private browsing mode}
Private browsing mode exists in all major browsers, but has no standard
behavior~\cite{ABBJ10}.
Interaction with extensions, treatment of cookies, history, and
bookmarks upon entering and exiting are different across browsers.
\begin{comment}
For example, entering private browsing in Firefox does not clear
cookies, history, or other session data; session data is cleared on exiting
private browsing mode. In contrast, incognito mode in Chrome makes previous
session state unavailable and clears new session state on exit; this mode
may be preferable as a ``Guest mode'' where the device owner does not want the
guest to either view or pollute existing state.
\end{comment}
Similar to multiple profiles, private browsing mode is not secure against local
attacks.

@@

\subsubsection{Linking identities}

For many users, the natural separation that occurs when creating multiple
accounts, using multiple browsers and devices is a drawback, not a benefit.
These users want fewer contextual identities and use the following techniques
to merge them.

\paragraph{Linking between profiles}

@@

\subsubsection{Curating identities}

\paragraph{Auditing} Wang et. al suggest that common techniques
for handling regret online include manual deletion of regret-
table posts, self-censoring or delaying posts that they predict
might bring regret~\cite{wang}. Pew Internet reports that 57\% of Internet
users periodically search for themselves to manage reputation, with young
adults being the most active~\cite{pew3}.

\subsection{How can we improve identity management tools?}

Service providers are highly incentivized to make linking identities easy, so
we concentrate on tools to help separate and curate identities.

\begin{comment}
\paragraph{Automatically inferring identities}
A contextual identity may be based on tasks and relationships.
Browsing activity is a rich source of information for inferring tasks.  For
example, the \texttt{about:profile} Firefox extension uses the Open Directory
Project and Alexa to categorize URLs that the user has
visited~\cite{aboutprofile}.

Tang et al.~show that most people do not take the time to create labels and
maintain friend lists~\cite{tang}. However, the same authors show how to use
heterogeneous networks to infer relationship types (e.g., manager-subordinate)
though the graph itself is unlabeled.

\paragraph{Mitigating implicit linkage}
Given a user's contextual identities, we may be able to prevent information
leakage between them.  For example, preventing third-party cookies from being
read and set across task boundaries means that targeted ads for dating would
not follow the user when visiting a technology news site. Knowing the user's
current contextual identity also allows the browser to suppress URL bar
suggestions that aren't relevant to that identity, protecting the user from
both shoulder-surfing and distraction.
\end{comment}

\paragraph{Mitigating explicit linkage} Federated login services can prevent
linking contextual identities to the same user identifier.  For example, a
federated login service that supported multiple identifiers could prevent the
user from associating the same identifier to radically different
contextual identities, such as ones for dating and professional use.

\paragraph{Auditing}
A browser is in an ideal position to intermediate social network
posts, aggregate them locally, and present them to the user when they desire to
audit their digital footprint.  For example, a user could see all of the
comments and posts they made in the last week and redact content that is
sensitive or too negative, a frequent cause of regret~\cite{wang}. 
Such a tool could incorporate sentiment analysis to aid the user in finding
particularly problematic content.

\paragraph{Expiring posts}
Humans don't have perfect memories, so perhaps social networks shouldn't either
~\cite{delete}. Many users already engage in manual auditing and deletion
of old posts~\cite{fbtips2}. A better solution would be to build tools that let
the user manage this more easily through an API: both Twitter and Facebook
provide APIs for post deletion\footnote{Google Plus offers a read-only API.}.

\paragraph{Expiring contextual identities}
Engaging in a long-term task such as house-buying
often requires the construction of a contextual identity. The tasks associated
with this identity have an externally imposed end date and may have long-lived
side-effects, such as long-term cookies that reveal sensitive information
(e.g., the neighborhood of the house purchase, income information derived from
purchases, other demographic data). For contextual identities that have
outlived their usefulness, users would benefit from destruction of side-effects
such as cookie data and service accounts.
